### 2020-04-08 paper/spores.tex
Reorganizes files to have SPORES in spores.tex

\documentclass{article}
\input{preamble.tex}
\usepackage{authblk}

\begin{document}
\title{%
  \acs*{SPORES}: \acl*{SPORES}%
  %\name: Stateless Predictive Onion Routing for E-Squads%
  %% From the IEEE template
  % \thanks{Identify applicable funding agency here. If none, delete this.}
  % \thanks{%
  %   Daniel Bosk and Sonja Buchegger were funded by
  %   the Swedish Foundation for Strategic Research grant SSF FFL09-0086.
  %   Research done while Daniel Bosk visited the WIDE team at INRIA/IRISA Rennes, 
  %   France.
  % }
}

\author[1]{Daniel Bosk\thanks{%
  Research done while the author visited the WIDE team at INRIA/IRISA Rennes, 
  France.
}}
\affil[1]{KTH Royal Institute of Technology\\\email{daniel@bosk.se}}
\author[1]{Sonja Buchegger}
\author[2]{Adrien Luxey}
\affil[2]{Univ.\ de Rennes, INRIA, CNRS, IRISA\\\email{Adrien.Luxey@irisa.fr}}
\author[2]{Yérom-David Bromberg}
\author[2]{François Taïani}

\mode<article>{\maketitle}
\mode<presentation>{%
  \begin{frame}
    \maketitle
  \end{frame}
}

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\input{contents.tex}
\end{document}

>>>>

%!TEX root = spores.tex

\section{Design of the \name file transfer system}%
\label{design}

% \sonja{will frame and structure (A) squad overlay (prediction) (B)
%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
%   if not included earlier (F) out-of-band}
% \commentDaniel{I suggest the following structure:
%   (A) SphinxES
%   (B) SPOR (global overlay)
%   (C) SPORES (local overlay).
%   My original idea was to make SphinxES its own section before the design 
%   section instead of a subsection in the design section.}

%\include*{spor}
%\include*{squad-overlay-design}
\include*{file-transfer-design}
